Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-27 sections/eval.tex
Update on Overleaf.

Sparse Matrix-Matrix Multiplication (SpGEMM) is a fundamental operation in scientific computing and data analytics. SpGEMM focuses on efficiently computing the product of two sparse matrices to produce an output sparse matrix.
The inner-product, outer product, and Gustavson's algorithm are three different approaches to performing SpGEMM. 
Inner-product involves multiplying two matrices by taking dot products of corresponding rows and columns.
Outer-product computes the product of all pairs of elements from the input matrices.
More detailed explanation is available in Section 2.2 of ~\cite{zhang2021gamma}.
Figures ~\ref{spgemm_small} and ~\ref{spgemm_large} show SpGEMM results with Finch and TACO.
Note that inner-product is very inefficient unless sparse matrices are nearly dense because the cost of inner-product is dominated by the cost of intersection

>>>>

Sparse Matrix-Matrix Multiplication (SpGEMM) is a fundamental operation in scientific computing and data analytics. SpGEMM focuses on efficiently computing the product of two sparse matrices to produce an output sparse matrix.
The inner-product, outer product, and Gustavson's algorithm are three different approaches to performing SpGEMM. 
Inner-product involves multiplying two matrices by taking dot products of corresponding rows and columns.
Outer-product computes the product of all pairs of elements from the input matrices.
More detailed explanation is available in Section 2.2 of ~\cite{zhang2021gamma}.
Figures ~\ref{spgemm_small} and ~\ref{spgemm_large} show SpGEMM results with Finch and TACO.
Note that inner-product is very inefficient unless sparse matrices are nearly dense because the cost of intersections that incurs a lot of redundant comput
